---
title: "Assignment 4"
author: "Max Diamond and Mauricio Collado"
date: "11/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

# 1. Introduction

Talk about citation 

# 2. Data and methods

Describe

# 3. Results

## 3.1 Evolution of lobster counts

Since they started to be a MPA (2016 and 2017), the lobster count has a rising trend.

Remember carapace size. 

```{r}
#1. Attach relevant packages

library(tidyverse)
library(janitor)
library(here)
library(dplyr)
library(lubridate)
library(tidyr)
library(effsize)
library(kableExtra)

#We read the lobster dataset, correct NA, clean names and, just in case, lubridate some data.

lobster_abundance <- read_csv(here::here("lobster_abundance_sbc_lter.csv"), 
                              na="-99999") %>% # We correct the NA format.
  clean_names() %>% # We correct the columns names
  mutate(MPA = ifelse(site == "IVEE", "MPA",
                    ifelse(site == "NAPL", "MPA","non MPA")))

#lobster_date$MPA = ifelse(site=="IVEE"| site=="NAPL","MPA","non MPA")

# We consider the observations counts in each transect

lobster_counts <- lobster_abundance %>% 
  group_by(site, year, MPA) %>% # We keep site and year. What about MPA and non MPA?
  summarize(total_counts=sum(count))   #We sum all the observations
  #tidyr::uncount (count)

#We create the graph

ggplot(lobster_counts, aes(x=year, y=total_counts, group=site, colour=site)) + # We group and color by site
  geom_line()+ #we create our line graph
  # We add the main title and axis labels
  labs(x="Years", 
       y="Total lobsters counts per year", 
       title="Graph 1: Total lobster counts by site, 2012-2018") +
  theme_minimal() + #We select the theme minimal
  facet_wrap(~MPA)


# correct caption
# correct legend

```

## 3.2 Lobster size distribution

Analysis of

```{r}

# We create distibution graphs for lobster size

lobster_compare <- lobster_abundance %>% # We create the dataset to compare
  filter(year %in% c(2012, 2018)) #We filter the relevant years to compare

ggplot() +
  geom_violin(data=lobster_compare[which(lobster_compare$year==2012),], aes(x=site, y=size_mm), fill="gray", alpha=0.4) +
  geom_violin(data=lobster_compare[which(lobster_compare$year==2018),], aes(x=site, y=size_mm), fill="red", alpha=0.5) +
  labs(x="Site", 
       y="Lobster carapace size (mm)", 
       title="Graph 2: Distribution of lobster carapace size by site, 2012-2018")
  

# DRAW QUANTILES
# Separate site and year
# Add format


```

## 3.3 Test

```{r}
# we create lobster data for each year MPA category


# Dataset year 2012 and for MPA sites
lobster_2012_MPA <- lobster_compare %>% 
  filter(year==2012, MPA=="MPA") %>% 
  select(year, size_mm, MPA)

# Dataset year 2012 and for non MPA sites
lobster_2012_non <- lobster_compare %>% 
  filter(year==2012,  MPA=="non MPA") %>% 
  select(year, size_mm, MPA)

# Dataset year 2018 and for MPA sites
lobster_2018_MPA <- lobster_compare %>% 
  filter(year==2018, MPA=="MPA") %>% 
  select(year, size_mm, MPA)

# Dataset year 2018 and for non MPA sites
lobster_2018_non <- lobster_compare %>% 
  filter(year==2018,  MPA=="non MPA") %>% 
  select(year, size_mm, MPA)

# Basic statistics

# Sample size 
MPA_2012 <- sum(!is.na(lobster_2012_MPA$size_mm))
non_2012 <- sum(!is.na(lobster_2012_non$size_mm))
MPA_2018 <- sum(!is.na(lobster_2018_MPA$size_mm))
non_2018 <- sum(!is.na(lobster_2018_non$size_mm))

# Means 
MPA_2012_mean <- mean(lobster_2012_MPA$size_mm, na.rm = TRUE)
non_2012_mean <- mean(lobster_2012_non$size_mm, na.rm = TRUE)
MPA_2018_mean <- mean(lobster_2018_MPA$size_mm, na.rm = TRUE)
non_2018_mean <- mean(lobster_2018_non$size_mm, na.rm = TRUE)

# Medians 
MPA_2012_median <- median(lobster_2012_MPA$size_mm, na.rm = TRUE)
non_2012_median <- median(lobster_2012_non$size_mm, na.rm = TRUE)
MPA_2018_median <- median(lobster_2018_MPA$size_mm, na.rm = TRUE)
non_2018_median <- median(lobster_2018_non$size_mm, na.rm = TRUE)

# Standard deviations 
MPA_2012_sd <- sd(lobster_2012_MPA$size_mm, na.rm = TRUE)
non_2012_sd <- sd(lobster_2012_non$size_mm, na.rm = TRUE)
MPA_2018_sd <- sd(lobster_2018_MPA$size_mm, na.rm = TRUE)
non_2018_sd <- sd(lobster_2018_non$size_mm, na.rm = TRUE)


```


#### Graph 4: General Stats by MPA category and year
```{r}
# We create the dataframe for the general stats table
text_general_stats <- data.frame(
  Items = c("MPA 2012", "Non MPA 2012", "MPA 2018", "Non MPA 2018"),
  Observations = c(MPA_2012, non_2012, MPA_2018, non_2018), 
  Mean = c(MPA_2012_mean, non_2012_mean, MPA_2018_mean, non_2018_mean), 
  Median = c(MPA_2012_median, non_2012_median, MPA_2018_median, non_2018_median), 
  StandardDeviation = c(MPA_2012_sd, non_2012_sd, MPA_2018_sd, non_2018_sd) 
)

# We draw the table
kable(text_general_stats) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```



```{r}
# QQ plot MISSING!!!

# 2012 MPA vs non MPA

# T test
MPA_versus_non_2012_test = t.test(lobster_2012_MPA$size_mm,lobster_2012_non$size_mm, paired=FALSE)
#MPA_versus_non_2012_test

# Cohen test
MPA_versus_non_2012_d = effsize::cohen.d(lobster_2012_MPA$size_mm,lobster_2012_non$size_mm, na.rm=TRUE)
#MPA_versus_non_2012_d

# 2018 MPA vs non MPA

# T test
MPA_versus_non_2018_test = t.test(lobster_2018_MPA$size_mm, lobster_2018_non$size_mm, paired=FALSE)
#MPA_versus_non_2018_test


# Cohen test
MPA_versus_non_2018_d = effsize::cohen.d(lobster_2018_MPA$size_mm, lobster_2018_non$size_mm, na.rm=TRUE)
#MPA_versus_non_2018_d

#////////////////////////////////////////////////////////////
#////////////////////////////////////////////////////////////
# MPA 2012 vs 2018
MPA_versus_2012_2018_test = t.test(lobster_2018_MPA$size_mm,lobster_2012_MPA$size_mm, paired=FALSE)
#MPA_versus_2012_2018_test 

# Cohen test
MPA_versus_2012_2018_d = effsize::cohen.d(lobster_2018_MPA$size_mm,lobster_2012_MPA$size_mm, na.rm=TRUE)
#MPA_versus_2012_2018_d

# non MPA 2012 vs 2018
non_versus_2012_2018_test = t.test(lobster_2018_non$size_mm, lobster_2012_non$size_mm, paired=FALSE)
#non_versus_2012_2018_test 

# Cohen test
non_versus_2012_2018_d = effsize::cohen.d(lobster_2018_non$size_mm,lobster_2012_non$size_mm, na.rm=TRUE)
#non_versus_2012_2018_d

```


#### Graph 6: Tests on lobster size comparing MPA category by year
```{r}
# Table of hypothesis MPA vs non MPA
text_hypothesis <- data.frame(
  Items = c("MPA vs non MPA 2018", "MPA vs non MPA 2012"),
  "Mean MPA" = c(MPA_versus_non_2012_test$estimate[1], 
                 MPA_versus_non_2018_test$estimate[1]), 
  "Mean non MPA" = c(MPA_versus_non_2012_test$estimate[2], 
                     MPA_versus_non_2018_test$estimate[2]), 
  "P-value" = c(MPA_versus_non_2012_test$p.value, 
                MPA_versus_non_2018_test$p.value), 
  "Cohen test" = c(MPA_versus_non_2012_d$estimate, 
                   MPA_versus_non_2018_d$estimate)
)

kable(text_hypothesis) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)

# rm(list = ls())
```


#### Graph 7: Tests on lobster size comparing years by MPA category

```{r}

# Table of hypothesis MPA vs non MPA
text_hypothesis2 <- data.frame(
  Items = c("MPA 2018 vs 2012", "Non MPA 2018 vs 2012"),
  "Mean 2018" = c(MPA_versus_2012_2018_test$estimate[1], 
                 non_versus_2012_2018_test$estimate[1]), 
  "Mean 2012" = c(MPA_versus_2012_2018_test$estimate[2], 
                    non_versus_2012_2018_test$estimate[2]), 
  "P-value" = c(MPA_versus_2012_2018_test$p.value, 
                non_versus_2012_2018_test$p.value), 
  "Cohen test" = c(MPA_versus_2012_2018_d$estimate, 
                   non_versus_2012_2018_d$estimate)
)

kable(text_hypothesis2) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)

# rm(list = ls())
```


# 4. Conclusions and recommendations

# References
